---
title: "PackageCitation"
author: "Benjamin Michael Marshall"
date: "`r Sys.Date()`"
output: html_document
bibliography: [multiverse_refs.bib, packages_refs.bib]
---
```{r pcks, include=TRUE}
pcks <- grateful::scan_packages(cite.tidyverse = FALSE, dependencies = TRUE,
                                omit = c("multiverseHabitat"))

additionalVec <- c("osfr",
                   "move", "ctmm", "adehabitatHS", "amt", 
                   "abmAnimalMovement")
# "NLMR" is in the main references manually because of non unicode characters
additionalPcks <- data.frame("pkg" = additionalVec,
                             "version" = unlist(lapply(additionalVec, function(x){as.character(packageVersion(x))})))

pcks <- rbind(pcks, additionalPcks)
```
```{r citeGen, include=TRUE}

grateful::cite_packages(
  output = "citekeys",
  out.dir = here::here("notebook", "manuscript"),
  pkgs = pcks$pkg,
  cite.tidyverse = FALSE,
  dependencies = TRUE,
  include.RStudio = TRUE,
  bib.file = "packages_refs.bib")

```

In addition to packages already mentioned in the methods we also used the following.

We used *R* `r paste0("v.", version$major, ".", version$minor)` [@base] via *RStudio* v.`r rstudioapi::versionInfo()$version` [@rstudio].
We used *here* `r paste0("v.", packageVersion("here"))` [@here] and *qs* `r paste0("v.", packageVersion("qs"))` [@qs] to manage directory addresses and saved objects.

We used *raster* `r paste0("v.", packageVersion("raster"))` [@raster] and *RandomFields* `r paste0("v.", packageVersion("RandomFields"))` [@RandomFields] to aid landscape raster creation alongside NLMR `r paste0("v.", packageVersion("NLMR"))` [@NLMR].

We used *ggplot2* `r paste0("v.", packageVersion("ggplot2"))` for creating figures [@ggplot2], with the expansions: *patchwork* `r paste0("v.", packageVersion("patchwork"))` [@patchwork], *ggridges* `r paste0("v.", packageVersion("ggridges"))` [@ggridges], and *ggdist* `r paste0("v.", packageVersion("ggdist"))` [@ggdist].

We used *brms* `r paste0("v.", packageVersion("brms"))` [@brms] to run Bayesian models, with dianogistics generated used *bayesplot* `r paste0("v.", packageVersion("bayesplot"))` [@bayesplot], *tidybayes* `r paste0("v.", packageVersion("tidybayes"))` [@tidybayes], and *performance* `r paste0("v.", packageVersion("performance"))` [@performance].

We used the *dplyr* `r paste0("v.", packageVersion("dplyr"))` [@dplyr], *tibble* `r paste0("v.", packageVersion("tibble"))` [@tibble], *reshape2* `r paste0("v.", packageVersion("reshape2"))` [@reshape2], and *stringr* `r paste0("v.", packageVersion("stringr"))` [@stringr] packages for data manipulation.

We used *sp* `r paste0("v.", packageVersion("sp"))` [@sp], *adehabitatHR* `r paste0("v.", packageVersion("adehabitatHR"))` [@adehabitatHR], *move* `r paste0("v.", packageVersion("move"))` [@move] for manipulation of spatial data and estimation of space use not otherwise mentioned in the methods.

We used rmarkdown `r paste0("v.", packageVersion("rmarkdown"))` [@rmarkdown2022; @rmarkdown2018; @rmarkdown2020], bookdown `r paste0("v.", packageVersion("bookdown"))` [@bookdown2016; @R-bookdown], tinytex `r paste0("v.", packageVersion("tinytex"))` [@tinytex2019; @tinytex2022], and knitr `r paste0("v.", packageVersion("knitr"))` [@knitr2015; @knitr2014; @knitr2022] packages to generate type-set outputs.

We generated R package citations with the aid of *grateful* `r paste0("v.", packageVersion("grateful"))` [@grateful].
